Trends of SDR in Thessaloniki

### 2023-06-09 Article.Rmd
Commit 2023-06-09 17:17

site location description and aerosols effect

@@

Before further analysis, we implement an appropriate aggregation scheme on the 1-minute data, to preserve the ....representabiliyt....
When we use daily mean values we exclude instances with less than `r Daily_aggregation_N_lim` valid data points.
Accordingly, monthly values are computed from the daily aggregated data, where months with less than `r Monthly_aggegation_N_lim` days are rejected. 
The daily seasonal values are indexed based on the day of year number, and the monthly by the corresponding calendar month.

<!-- Seasonal -->
For the seasons of the year trends, we also grouped the mean daily values by season (December - February: Winter, March - May: Spring, etc.)

<!-- Deseasonalization -->
Finally, for each data set, we remove the natural occurring seasonal variation.
This is done, by calculating the mean values for the appropriate time step, and subtracting the annual cycle from the actual data.
Thus, for each data set we have obtained the relative departure of the seasonal mean.
These values are presented in the following section.

>>>>

Site location description and aerosols effect

@@

<!-- aggregation -->
Before further analysis and Deseasonalization, we implement an appropriate aggregation scheme on the 1-minute data. To preserve the representativeness we use the following criteria:
a) for daily mean values we exclude instances with less than `r Daily_aggregation_N_lim` valid data points,
b) accordingly, monthly values are computed by daily aggregated data, where months with less than `r Monthly_aggegation_N_lim` days are rejected. 
The daily seasonal values were indexed based on the day of year number, and the monthly by the corresponding calendar month.
<!-- Seasonal -->
For the seasons of the year trends, we grouped the mean daily values by season (December - February: Winter, March - May: Spring, etc.).
<!-- Deseasonalization -->
Finally, for each data set, we remove the natural occurring seasonal variation.
This is done, by calculating the mean values for the appropriate time step, and subtracting the annual cycle from the actual data.
Thus, for each data set we have obtained the relative departure of the seasonal mean.
These values are presented in the following section.
